Visualization of [fulle name] Fractional Integrals

### 2019-05-28 fractional/CMJ style files/article-template.tex
added a new article

\noindent
The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876,laurent1884}. Fractional calculus has now developed into a mature discipline \cite{machado14}. 
However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability. At the first international conference on fractional calculus in
New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}. Subsequently, the last few decades has seen 
a number of papers that attempt to rectify this. There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95} and economic 
interpretations \cite{tarasova17} of fractional order integrals and differentials.\\

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral \cite{laurent1884}.
As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
We, however, deem thhese definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. The geometric interpretation 
we present here is an extension of the geometric interpretation presented by Podlubny\cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the are obtained by summing toghether 
the area of an infinite number of non-rectangular infinitesimels, i.e. a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,?}. Combining these two ideas together results in the following geometric 
interpretation: the Riemann-Liouville fractional integral can be interpreted as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\

\noindent
We specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and 
as such we will try to steer clear from using too many mathematical definitions and proofs. We will rather convey our ideas using as many examples as possible. From the 
three groups mentioned we believe that the undergraduate student will find this article the most useful. Although undergraduate students have a limited understanding of 
fractional calculus they generally are quite interested in the subject. This is quite evident from perusing mathematical social media platforms and from surveying 
articles published in undergraduate journals \cite{munkhammar05}. One of the reasons undergraduates struggle to grasp fractional calculus, apart from it not normally being taught as part of the undergraduate curricilum, is because, 
it is such an abstract concept. We believe that the geometric interpretation we present in this paper, as it is similar in nature to the definition of classical integration, will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental 
concepts that unerpin fractional calculus. We also hope that this paper will enable and encourage undergraduate lectures to already introduce students to this fascinating mathematical discipline as part of their 
undergraduate training.\\

\noindent
We start the paper by reviewing the definition of the Riemann-Stieltjes and Cavalieri integral. We then present the definition of the Riemann-Liouville fractional integral. 
We end the paper by presenting our novel geometric interpretation and a conclusion.

@@

\section{First-level section heading}

Section headings use an initial capital letter on the first word, with subsequent words lowercase.  In general, the style of the journal is to leave all section headings unnumbered.  Consult the journal editor if you wish to depart from this and other conventions.

\subsection{Second-level heading}

The same goes for second-level headings.  It is not necessary to add font commands to make the math within heads bold and sans serif; this change will occur automatically when the production style is applied.

\section{Graphics}

Figures for the \textsc{Journal} can be submitted as either color or black \& white graphics.  Generally, color graphics will be used for the online publication, and converted to black \& white images for the print journal.  We recommend using whatever graphics program you are most comfortable with, so long as the submitted graphic is provided as a separate file using a standard file format.

For best results, please follow the following guidelines:
\begin{enumerate}
\item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
\item Line art will reproduce best if provided in vector form, preferably EPS.
\item Alternatively, both photographs and line art can alternatively be provided as PDF files.  Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
\item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.  In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Journal} can be delivered in e-reader formats.
\item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.  If possible, avoid photographs that have excess shadows or glare.
\end{enumerate}

\section{Theorems, definitions, proofs, and all that}

Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.

\begin{theorem}[Pythagorean Theorem]
Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
\end{theorem}

\begin{proof}
Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.  When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
\end{proof}

\begin{definition}[Secant Line]
Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
\end{definition}

\begin{remark}
Remarks stylize the same as definitions.
\end{remark}

Note that the \textit{College Mathematics Journal\/} is meant to be accessible to a broad audience, so heavy use of theorem-like formalisms is generally discouraged.

>>>>

\noindent
The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
of the theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876,laurent1884}. Fractional calculus has now developed into a mature discipline \cite{machado14}. 
However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability. At the first international conference on fractional calculus in
New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}. Subsequently, the last few decades has seen 
a number of papers that attempt to rectify this. There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95} and economic 
interpretations \cite{tarasova17} of fractional order integrals and differentials.\\

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral \cite{laurent1884}.
As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. Furthermore, the geometric interpretation 
we present here is an extension of the geometric interpretation presented by Podlubny \cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area whis is obtained by summing toghether 
the area of an infinite number of non-rectangular infinitesimels, i.e. a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,?}. Combining these two ideas together results in the following geometric 
interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\

\noindent
It should be noted that we specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and 
as such we will try to steer clear from using too many mathematical definitions and proofs. We will rather convey our ideas using as many examples as possible. From the 
three groups mentioned we believe that the undergraduate student will find this article the most useful. Although undergraduate students have a limited understanding of 
fractional calculus they generally are quite interested in the subject. This is quite evident from perusing mathematical social media platforms and from surveying 
articles published in undergraduate journals \cite{munkhammar05}. Undergraduates struggle to grasp fractional calculus, because it is very abstract. We believe that the geometric interpretation we present in this paper, as it is similar in nature to the definition of classical integration, will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental 
concepts that unerpin fractional calculus.\\

%We also hope that this paper will enable and encourage lectures to teach this fascinating mathematical discipline to undergraduate students.\\

\noindent
We start the paper by reviewing the definition of the Riemann-Stieltjes integreal, the Cavalieri integral and the Euler function. We then present the definition of the Riemann-Liouville fractional integral. 
We end the paper by presenting our novel geometric interpretation, some examples and a conclusion.

@@

% \section{First-level section heading}
% 
% Section headings use an initial capital letter on the first word, with subsequent words lowercase.  In general, the style of the journal is to leave all section headings unnumbered.  Consult the journal editor if you wish to depart from this and other conventions.
% 
% \subsection{Second-level heading}
% 
% The same goes for second-level headings.  It is not necessary to add font commands to make the math within heads bold and sans serif; this change will occur automatically when the production style is applied.
% 
% \section{Graphics}
% 
% Figures for the \textsc{Journal} can be submitted as either color or black \& white graphics.  Generally, color graphics will be used for the online publication, and converted to black \& white images for the print journal.  We recommend using whatever graphics program you are most comfortable with, so long as the submitted graphic is provided as a separate file using a standard file format.
% 
% For best results, please follow the following guidelines:
% \begin{enumerate}
% \item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
% \item Line art will reproduce best if provided in vector form, preferably EPS.
% \item Alternatively, both photographs and line art can alternatively be provided as PDF files.  Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
% \item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.  In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Journal} can be delivered in e-reader formats.
% \item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.  If possible, avoid photographs that have excess shadows or glare.
% \end{enumerate}
% 
% \section{Theorems, definitions, proofs, and all that}
% 
% Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.
% 
% \begin{theorem}[Pythagorean Theorem]
% Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
% \end{theorem}
% 
% \begin{proof}
% Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.  When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
% \end{proof}
% 
% \begin{definition}[Secant Line]
% Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
% \end{definition}
% 
% \begin{remark}
% Remarks stylize the same as definitions.
% \end{remark}
% 
% Note that the \textit{College Mathematics Journal\/} is meant to be accessible to a broad audience, so heavy use of theorem-like formalisms is generally discouraged.
